---
title: "plotly"
author: "Maisie Sun"
date: "2022-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

library(plotly)
```

## Data

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500) %>%
  drop_na(rating)
```

## Scatterplot

```{r}
nyc_airbnb %>%
  mutate(
    text_label = str_c("Price: ", price, "\nRating: ", rating)
  ) %>%
  plot_ly(
    x = ~lat, y = ~long, color = ~price,
    type = "scatter", mode = "markers",
    alpha = .5, text = ~text_label
  )
```

## Boxplot

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

double click on name to only see that boxplot
single click on name to see everything except that boxplot

## Barplot

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

Must have `count`: number of obs for each neighborhood for height of bargrpah

More graphs: https://plotly.com/r/

## ggplot

```{r}
scatter_ggplot = 
  nyc_airbnb %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```

This is helpful because it is often quicker to make graphics using ggplot
issues: slower, less appealing for users

* if it's for yourself, this is fine

* if it's for someone else, use the plotly
